---
title: SUR demo
output: github_document
bibliography: ../../blog_181126/content/post/add.bib
---

> Systems of regression equations have been a hallmark of econometrics for severaldecades. Standard examples include seemingly unrelated regressions andvarious macroeconomic simultaneous equation models. The package systemfit(Henningsen and Hamann 2007) can estimate a number of multiple-equationmodels. As an example, we present a seemingly unrelated regression (SUR)model (Zellner 1962) for the Grunfeld data. As noted by Greene (2003, p. 329, fn. 39), “[a]lthough admittedly not current, these data are unusually cooperativefor illustrating the di???erent aspects of estimating systems of regressionequations”. Unlike the panel data models considered in the preceding section, which permit only individual-specific intercepts, the SUR model also allowsfor individual-specific slopes. (As regards terminology, the “individuals” of thepreceding section will now be referred to as “equations”.) The model assumescontemporaneous correlation across equations, and thus joint estimation of allparameters is, in general, more efficient than OLS on each equation.

参考 @Kleiber2008Applied

```{r setup}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

```{r}
library(systemfit)
library(plm)
data("Grunfeld", package = "AER")
gr2 <- subset(Grunfeld, firm %in% c("Chrysler", "IBM")) # Id 太多会很慢
pgr2 <- pdata.frame(gr2, c("firm", "year"))
# use of 'plm.data' is discouraged, better use 'pdata.frame' instead
gr_ols <- systemfit(invest ~ value + capital, method = "OLS", data = pgr2)
gr_sur <- systemfit(invest ~ value + capital, method = "SUR", data = pgr2)
summary(gr_ols, residCov = FALSE, equations = FALSE) # 展示每个id每个beta
summary(gr_sur, residCov = FALSE, equations = FALSE)
```
